Analysis of H-1B Visa Workers Using H-1B LCA Disclosure Data (2020–2024)

### 2025-03-14 products/manuscript/Manuscript.qmd
part 3 commit 1

## Statistical analysis
Various plots will be made to visualize the data. Linear regression will be used to analyze the relationship between variables. Machine learning methods will be used as modeling technique.

@@

The @fig-top10_soc_title displays the 10 job titles with the highest number of applications filed between 2020 and 2024, with "Software Developers, Applications" leading at over 500,000 cases. The @fig-top10_emp_name highlights the top 10 employers by application count, with "COGNIZANT TECHNOLOGY SOLUTIONS US CORP" topping the list at approximately 93,000 cases. The @fig-top10_emp_state presents the 10 states with the most applications, with California recording over 600,000 cases. Meanwhile, the @fig-distribution_PREV_WAGE plot illustrates the distribution of prevailing wages, revealing that most cases offer wages near $100,000 per year, while fewer cases fall at the lower end (around $15,000) or approach higher values near $800,000 (see Supplement Table 1).
```{r}
#| label: fig-top10_soc_title
#| fig-cap: "Top 10 Job Titles."
#| echo: FALSE
knitr::include_graphics(here("results","figures","top10_soc_title.png"))
```

@@

The @fig-wage_by_soc_title plot shows the 10 job titles with the highest median wage, and they are all medical practitioners. The @fig-wage_by_employer plot highlights the 10 employers with the highest median wage, spanning healthcare, financial services, life sciences, technology, and manufacturing. The @fig-wage_by_state plot indicates that Washington has the highest median wage by state. Plots for the 10 lowest median wages are provided in Supplement Figures 1–3. The @fig-remote_trend_absolute plot illustrates the trend of remote work over the years. The number of remote work cases surged from 2019 to 2020 due to the pandemic and remained relatively stable from 2020 to 2023. Post-pandemic, there was a slight decline from 2023 to 2024. However, as remote work patterns became more established, the decrease was not significant. This analysis uses absolute values instead of proportions because remote work is identified based on discrepancies between employer and worksite states. Some remote work cases may not be captured under this definition, potentially underestimating the actual proportion. Therefore, absolute values provide a more accurate reflection of the remote work trend.

@@

## Basic statistical analysis

>>>>

## Statistical analysis
Various plots were created to visualize the data. Classification models were used to analyze the categorical outcome.

@@

The @fig-top10_soc_title displays the 10 job titles with the highest number of applications filed between 2020 and 2024, with "Software Developers, Applications" leading at over 500,000 cases. The @fig-top10_emp_name highlights the top 10 employers by application count, with "COGNIZANT TECHNOLOGY SOLUTIONS US CORP" topping the list at approximately 93,000 cases. The @fig-top10_emp_state presents the 10 states with the most applications, with California recording over 600,000 cases. Meanwhile, the @fig-distribution_PREV_WAGE illustrates the distribution of prevailing wages, revealing that most cases offer wages near $100,000 per year, while fewer cases fall at the lower end (around $15,000) or approach higher values near $800,000 (see Supplement Table 1).
```{r}
#| label: fig-top10_soc_title
#| fig-cap: "Top 10 Job Titles."
#| echo: FALSE
knitr::include_graphics(here("results","figures","top10_soc_title.png"))
```

@@

The @fig-wage_by_soc_title shows the 10 job titles with the highest median wage, and they are all medical practitioners. The @fig-wage_by_employer highlights the 10 employers with the highest median wage, spanning healthcare, financial services, life sciences, technology, and manufacturing. The @fig-wage_by_state indicates that Washington has the highest median wage by state. Plots for the 10 lowest median wages are provided in Supplement Figures 1–3. The @fig-remote_trend_absolute illustrates the trend of remote work over the years. The number of remote work cases surged from 2019 to 2020 due to the pandemic and remained relatively stable from 2020 to 2023. Post-pandemic, there was a slight decline from 2023 to 2024. However, as remote work patterns became more established, the decrease was not significant. This analysis uses absolute values instead of proportions because remote work is identified based on discrepancies between employer and worksite states. Some remote work cases may not be captured under this definition, potentially underestimating the actual proportion. Therefore, absolute values provide a more accurate reflection of the remote work trend.

@@

## Basic statistical analysis
### Bivariate Analysis
The variable WAGE_RATE_OF_PAY_FROM was selected as the outcome of interest to study the wages of H-1B workers. I first conducted a bivariate analysis to identify potential predictor variables. To perform the analysis, I selected a half-month subset of the data.

The @fig-distribution_WAGE_Jan2024 illustrates a histogram of wage distribution during January 1–15, 2024. The continuous wage variable was categorized into four ranges: "(0, 75,000)", "(75,000, 150,000)", "(150,000, 225,000)", and "Above 225,000", converting it into a categorical variable.

A random forest model was applied for classification using a single predictor, with 1,380 observations in the training set and 346 observations in the testing set. @tbl-combined_accuracy1 to @tbl-combined_accuracy4 summarize the model fit for the predictors: job title (SOC_TITLE), employer location (EMPLOYER_STATE), worksite location (WORKSITE_STATE), and employer (EMPLOYER_NAME). The results indicate that these variables exhibit moderate predictive performance.

Next, a multivariate random forest model was developed. @tbl-combined_accuracy_all shows that the multivariate model outperformed the bivariate models.

In the next step, different classification algorithms will be explored to further enhance model performance. Additionally, cross-validation will be incorporated to improve model reliability.
```{r}
#| label: fig-distribution_WAGE_Jan2024
#| fig-cap: "Distribution of Wages (January 1–15, 2024)."
#| echo: FALSE
knitr::include_graphics(here("results","figures","distribution_WAGE_Jan2024.png"))
```

```{r}
#| label: tbl-combined_accuracy1
#| tbl-cap: "Model Fit for Wage Based on Job Title."
#| echo: FALSE
table1 = readRDS(here("results","tables","combined_accuracy1.rds"))
knitr::kable(table1)
```

```{r}
#| label: tbl-combined_accuracy2
#| tbl-cap: "Model Fit for Wage Based on Employer Locations."
#| echo: FALSE
table2 = readRDS(here("results","tables","combined_accuracy2.rds"))
knitr::kable(table2)
```

```{r}
#| label: tbl-combined_accuracy3
#| tbl-cap: "Model Fit for Wage Based on Worksite Locations."
#| echo: FALSE
table3 = readRDS(here("results","tables","combined_accuracy3.rds"))
knitr::kable(table3)
```

```{r}
#| label: tbl-combined_accuracy4
#| tbl-cap: "Model Fit for Wage Based on Employer."
#| echo: FALSE
table4 = readRDS(here("results","tables","combined_accuracy4.rds"))
knitr::kable(table4)
```

```{r}
#| label: tbl-combined_accuracy_all
#| tbl-cap: "Model Fit for Wage Based on Job Title, Employer Location, Worksite Location, and Employer."
#| echo: FALSE
table5 = readRDS(here("results","tables","combined_accuracy_all.rds"))
knitr::kable(table5)
```
